A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-15 mt-marathon.2013/PBML_article.tex
changes

Enabling ad-hoc features in Moses requires a framework where new feature functions can be easily added. Adding support for sparse features entails fundamental changes in the way features function scores are stored and calculated. It is generally known that MERT ??? is unstable with a large number of scores, using sparse features will also require tuning algorithms which are able to deal with a large, non-predetermined number of feature scores.

@@

The built-in feature functions in the phrase-based models are:
\begin{itemize}
  \item Translation model
  \item Language model
  \item Distortion model
  \item Lexicalized reordering model
  \item Word penalty
  \item Unknown word penalty
\end{itemize}

The hierarchical and syntax model also uses these feature functions, except for the distortion and lexicalized reordering model.

>>>>

Enabling ad-hoc features in Moses requires a framework where new feature functions can be easily added. Adding support for sparse features entails fundamental changes in the way features function scores are stored and calculated. It is generally known that MERT\cite{Och:MERT} is unstable with a large number of scores, using sparse features will also require tuning algorithms which are able to deal with a large, non-predetermined number of feature scores.

@@

The standard feature functions in the phrase-based models are:
\begin{itemize}
  \item Translation model
  \item Language model
  \item Distortion model
  \item Lexicalized reordering model
  \item Word penalty
  \item Unknown word penalty
\end{itemize}
The hierarchical and syntax model also uses these feature functions, except for the distortion and lexicalized reordering model.
